\textsf{Cyp2SQL -- Documentation}

### 2017-08-21 docs/latex/draftB.tex
Updated schema conversion unit to handle REALs and BOOLEANs.
Bug fixes and more testing and improved documentation.

\usepackage[hmargin={3 cm,3cm},top=1.5cm, marginpar=3cm]{geometry}
\usepackage{graphicx}
\usepackage{hyperref}
\hypersetup{colorlinks, linkcolor=blue, urlcolor=blue}
\usepackage{multicol}
\usepackage{lipsum}
\usepackage{xcolor}
\usepackage{pdfpages}
\usepackage{listings}
\definecolor{mauve}{rgb}{0.58,0,0.82}
\definecolor{dkgreen}{rgb}{0,0.6,0}
\lstdefinestyle{DOS}
{
backgroundcolor=\color{gray},
basicstyle=\color{white}\ttfamily,
breaklines=true,
postbreak=\mbox{\textcolor{red}{$\hookrightarrow$}\space}
}

@@

The codebase is entirely Java. There are some additional features provided through the ANTLR tool, as described in \S \ref{sec:antlr}. There are some script/.bat files that help the tool execute SQL on Postgres and pipe the results back into the tool.

\subsection{Quick usage}
Using the \texttt{cyp2sql-next.jar} file:
\begin{verbatim}
<-schema|-translate|-s|-t> <propertiesFile> <targetDatabaseName> <-dp|-dn|-r>
\end{verbatim}

\begin{center}
\begin{tabular}{ p{3cm} p{10.5cm} }
\texttt{-s \textbar{} -schema} & Runs the tool for schema conversion. See \S \ref{sec:schemaConv}. \\
\texttt{-t \textbar{} -translate} & Runs the tool for query translation. See \S \ref{sec:tranQ}. \\
\texttt{propertiesFile} & Path of the properties file \texttt{c2s\_props.properties}. See \S \ref{ss:prop}. \\
\texttt{targetDatabaseName} & Name of the relational database for either the converted graph schema to be stored into, or for the translated queries to execute on. \\
\texttt{dp \textbar{} -dn \textbar{} -r} & \textbf{Only needed when in query translation mode}.
\end{tabular}
\end{center}

@@

\begin{lstlisting}[language=Java, breaklines=true]
import database.postgres.InsertSchemaPostgres;
import intermediate_rep.DecodedQuery;
import production.C2SMain;
import production.C2SProperties;
import schema_conversion.SchemaConvert;

@@

@@

@@

\section{Translation of queries}
\label{sec:tranQ}
\subsection{Usage}
The tool requires a running Neo4j instance to be up and running.

>>>>

\usepackage[hmargin={3cm,3cm},top=1.5cm, marginpar=3cm]{geometry}
\usepackage{graphicx}
\usepackage{hyperref}
\hypersetup{colorlinks, linkcolor=blue, urlcolor=blue}
\usepackage{multicol}
\usepackage{lipsum}
\usepackage{xcolor}
\usepackage{pdfpages}
\usepackage{listings}
\definecolor{mauve}{rgb}{0.58,0,0.82}
\definecolor{dkgreen}{rgb}{0,0.6,0}
\lstdefinestyle{DOS}
{
backgroundcolor=\color{gray},
basicstyle=\color{white}\ttfamily,
breaklines=true,
postbreak=\mbox{\textcolor{red}{$\hookrightarrow$}\space}
}

@@

The source code is entirely Java and is built using Maven. There are some additional features provided through the ANTLR tool, as described in \S \ref{sec:antlr}. There are some script/.bat files that help the tool execute SQL on Postgres and pipe the results back into the \emph{Cyp2SQL} tool.

\subsection{Quick usage}
Using the \texttt{cyp2sql-next.jar} file from the command line:
\begin{verbatim}
<-schema|-translate|-s|-t> <propertiesFile> <targetDatabaseName> <-dp|-dn|-r>
\end{verbatim}

\begin{center}
\begin{tabular}{ p{3cm} p{10.5cm} }
\texttt{-s \textbar{} -schema} & Runs the tool for schema conversion. See \S \ref{sec:schemaConv}. \\
\texttt{-t \textbar{} -translate} & Runs the tool for query translation. See \S \ref{sec:tranQ}. \\
\texttt{propertiesFile} & Path of the properties file \texttt{c2s\_props.properties}. See \S \ref{ss:prop}. \\
\texttt{targetDatabaseName} & Name of the relational database for either the converted graph schema to be stored into, or for the translated queries to execute on. \\
\texttt{dp \textbar{} -dn \textbar{} -r} & \textbf{Only needed when in query translation mode}. See \S \ref{ssec:usage} for further details.
\end{tabular}
\end{center}

@@

\begin{lstlisting}[language=Java]
import database.postgres.InsertSchemaPostgres;
import intermediate_rep.DecodedQuery;
import production.C2SMain;
import production.C2SProperties;
import schema_conversion.SchemaConvert;

@@

The library and its dependencies can be added to a local Maven repository in the following way:

\begin{lstlisting}[language=bash, breaklines=true, postbreak=\mbox{\textcolor{red}{$\hookrightarrow$}\space}, backgroundcolor=\color{gray}, basicstyle=\color{white}\ttfamily]
$ git clone git@gitlab.dtg.cl.cam.ac.uk:fresco-projects/cyp2sql-next.git
$ cd cyp2sql-next
$ mvn install
\end{lstlisting}

@@

The tool can currently handle the following datatypes: \texttt{TEXT}, \texttt{INT}, \texttt{REAL}, \texttt{BOOLEAN}, and \texttt{TEXT[]}.

@@

\section{Translation of queries}
\label{sec:tranQ}
\subsection{Usage}
\label{ssec:usage}
The tool requires a running Neo4j instance to be up and running.
